A new metric for automatic discovery of periodic patterns in time series

### 2021-03-01 paper/main.Rmd
replace existing application with 8 households

elec$date_time <- as.Date(elec$date_time)

elec_linear <- elec %>% 
  ggplot() +
  geom_line(aes(x = date_time, y = kwh, group = time)) +
  facet_wrap(~id, nrow = 4, labeller = "label_both",
             strip.position =  "right",
             scales = "free_y") +
  theme_pubclean() 
#+
 # geom_rect(aes(xmin = as.Date("2018-02-01"), xmax = as.Date("2018-02-28"), ymin = -Inf, ymax = Inf),colour="white", size=0.5, alpha=0.02)

elec_zoom <-  elec %>% 
  filter(date >as.Date("2018-02-01") & date < (as.Date("2018-02-28"))) %>% 
  ggplot(aes(x=date_time, y = kwh)) +
  facet_wrap(~id, scales = "free_y", ncol = 1, strip.position =  "right") +
  geom_smooth() +
  geom_point(alpha = 0.5, size = 0.1) +
  gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")))

@@

dotplot
```

@@

elec <- read_rds(here("paper/data/elec_all-8.rds")) %>% 
  dplyr::filter(date(reading_datetime) >= ymd("20190701"), date(reading_datetime) < ymd("20191231"), meter_id==1) %>% 
  select(-meter_id) %>% 
  rename("id" = "household_id",
         "date_time" = "reading_datetime")

elec_linear <- elec %>% 
  ggplot() +
  geom_line(aes(x = date_time, y = kwh)) +
  facet_wrap(~id, nrow = 8, labeller = "label_both",
             strip.position =  "right",
             scales = "free_y") 
elec_linear
#+
 # geom_rect(aes(xmin = as.Date("2018-02-01"), xmax = as.Date("2018-02-28"), ymin = -Inf, ymax = Inf),colour="white", size=0.5, alpha=0.02)

# elec %>% dplyr::filter(date> as.Date("2018-02-01") & date<as.Date("2018-02-28"))

@@

dotplot <- elec_sig_split %>% 
  ggplot() +
  geom_point(aes(x = x_variable,
                 y = facet_variable, 
                 size = wpd, 
                 fill = significant),
             shape=21,
             alpha= 0.8) +
  scale_size_continuous() +
  theme(legend.position = "bottom") +
  scale_fill_viridis(discrete = TRUE, direction = 1) +
  facet_wrap(~id, nrow = 2) +
  guides(fill = guide_legend(), 
         size = guide_legend()) +
  theme_gray(base_size = 12, base_family = "Times") +
   theme(legend.position = "bottom")

dotplot
```

>>>>

elec_linear <- elec %>% 
  ggplot() +
  geom_line(aes(x = date_time, y = kwh)) +
  facet_wrap(~id, nrow = 4, labeller = "label_both",
             strip.position =  "right",
             scales = "free_y") +
  theme_pubclean() 
#+
 # geom_rect(aes(xmin = as.Date("2018-02-01"), xmax = as.Date("2018-02-28"), ymin = -Inf, ymax = Inf),colour="white", size=0.5, alpha=0.02)

elec_zoom <-  elec %>%
  filter(date >as.Date("2018-02-01") & date < (as.Date("2018-02-28"))) %>% 
  ggplot(aes(x=date_time, y = kwh)) +
  geom_line(alpha = 0.5, size = 0.1) +
  facet_wrap(~id, scales = "free_y", ncol = 1, strip.position =  "right") +
  gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")), unhighlighted_params = list(colour = "blue"))

@@

#myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))

heatplot <- elec_sig_split %>% 
  ggplot() +
  geom_tile(aes(x = x_variable,
                 y = facet_variable, 
                 fill = wpd)) + 
  scale_fill_gradient2() +
  theme(legend.position = "bottom") +
  facet_wrap(~id, nrow = 1) +
  coord_fixed() + 
  guides(fill = guide_legend()) +
  theme_void() +
  theme_gray(base_size = 12, base_family = "Times") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle = 60, hjust=1)
        , legend.position = "bottom")
  heatplot
```

@@

elec <- read_rds(here("paper/data/elec_all-8.rds")) %>% 
  dplyr::filter(date(reading_datetime) >= ymd("20190701"), date(reading_datetime) < ymd("20191231"), meter_id==1) %>% 
  select(-meter_id) %>% 
  rename("id" = "household_id",
         "date_time" = "reading_datetime") %>% 
  mutate(date = date(date_time))

elec_linear <- elec %>% 
  ggplot() +
  geom_line(aes(x = date_time, y = kwh),alpha = 0.7) +
  facet_wrap(~id, nrow = 8, labeller = "label_both",
             strip.position =  "right",
             scales = "free_y")

elec_zoom <-  elec %>%
  as_tibble() %>% 
  filter(date >as.Date("2019-09-01") & date < (as.Date("2019-09-30"))) %>% 
  ggplot(aes(x=date_time, y = kwh)) +
  geom_line(size = 0.1, colour = "blue") +
  facet_wrap(~id, 
             scales = "free_y",
             ncol = 1,
             strip.position =  "right") +
  gghighlight(date > as.Date("2019-09-15") & date < (as.Date("2019-09-21")), unhighlighted_params = list(colour = "black"))

elec_linear + elec_zoom

@@

heatplot <- elec_sig_split %>% 
  ggplot() +
  geom_tile(aes(x = x_variable,
                 y = facet_variable, 
                 fill = wpd)) + 
  scale_fill_gradient2() +
  theme(legend.position = "bottom") +
  facet_wrap(~id, nrow = 2) +
  coord_fixed() + 
  guides(fill = guide_legend()) +
  theme_void() +
  theme_gray(base_size = 12, base_family = "Times") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle = 60, hjust=1),legend.position = "bottom")
  heatplot
#            
# dotplot <- elec_sig_split %>% 
#   ggplot() +
#   geom_point(aes(x = x_variable,
#                  y = facet_variable, 
#                  size = wpd, 
#                  fill = significant),
#              shape=21,
#              alpha= 0.8) +
#   scale_size_continuous() +
#   theme(legend.position = "bottom") +
#   scale_fill_viridis(discrete = TRUE, direction = 1) +
#   facet_wrap(~id, nrow = 2) +
#   guides(fill = guide_legend(), 
#          size = guide_legend()) +
#   theme_gray(base_size = 12, base_family = "Times") +
#    theme(legend.position = "bottom")
```
